Improving the modelling of tempo and phoneme duration

### 2017-02-09 Paper/Paper_v1.tex
Kleine Änderungen an der PDF

We did compare speech rate considering only realized vowels/syllables and considering both realized and not realized syllables, as Koreman \cite{Koreman_2006} also did and...
Calculate also local speech rate.

>>>>

Koreman showed \cite{Koreman_2006} that the perceived speech rate is also influenced by the listener's knowledge of the expected articulations for a particular utterance, therefore it makes a difference if all expected phones are also articulated or not. Consequently, we did compare speech rate considering only articulated vowels/syllables, as well as considering both realized and intended syllables,  and tested both methods in our model.

Calculated also local speech rate.

We obtained the best approximation when using speech rate calculated as ...
